Supplementary Information: Quantifying the pathways to life using assembly spaces

### 2021-05-19 papers/assembly/I/main.tex
Start fresh on the definition of a basis

\tikzstyle{simple}=[-,line width=2.000]
\tikzstyle{arrow}=[-,postaction={decorate},decoration={markings,mark=at position .5 with {\arrow{>}}},line width=1.100]
\pgfdeclarelayer{edgelayer}
\pgfdeclarelayer{nodelayer}
\pgfsetlayers{edgelayer,nodelayer,main}

@@

\tikzstyle{empty}=[circle,fill=none, draw=none]
\tikzstyle{inputdot}=[circle,fill=black,draw=black, scale=.5]
\tikzstyle{dot}=[circle,fill=black,draw=black]
\tikzstyle{bounding}=[circle,dashed, fill=none,draw=black, scale=9.00]
\tikzstyle{simple}=[-,draw=black,line width=1.000]
\tikzstyle{arrow}=[-,draw=black,postaction={decorate},decoration={markings,mark=at position .5 with {\arrow{>}}},line width=1.000]
\tikzstyle{tick}=[-,draw=black,postaction={decorate},decoration={markings,mark=at position .5 with {\draw (0,-0.1) -- (0,0.1);}},line width=1.000]
\tikzstyle{inputarrow}=[->,draw=black, shorten >=.05cm]
\tikzstyle{sitemap}=[->, dashed, draw=red, ultra thick, shorten >=.05cm]
\tikzstyle{transitionmap}=[->, dashed, draw=blue, ultra thick, shorten >=.05cm]

@@

\newcommand{\upset}[1]{#1\!\!\uparrow}
\newcommand{\downset}[1]{#1\!\!\downarrow}
\newcommand{\N}{\mathbb{N}}
\newcommand{\B}{\mathcal{B}}
\newcommand{\Min}[1]{\min{(#1)}}
\newcommand{\A}{\mathcal{A}}
\newcommand{\powerset}{\mathcal{P}}

\newcommand{\red}[1]{{\color{red}#1}}
\newcommand{\TODO}[1]{\noindent\red{\textbf{TODO:}~#1}}

@@

@@

\begin{definition}\label{def:subnet}
    Let $Q$ be a Petri net. A \textbf{Petri subnet} $P$ of $Q$ consists of
    \begin{itemize}
        \item a subset of sites of $Q$, denoted $S(P)$
        \item a subset of transitions of $Q$, denoted $T(P)$
        \item a pair of maps $\begin{tikzcd}
                T(P)
                \arrow[r, shift left = 1, "\sigma_P"]
                \arrow[r, shift right = 1, "\tau_P", swap]
                &
                \N[S(P)]
        \end{tikzcd}$.
    \end{itemize}
    such that $\sigma_P = \sigma_Q|_{T(P)}$ and $\tau_P = \tau_Q|_{T(P)}$.
\end{definition}

@@

@@

Up to this point, all of the defintions have been fairly standard, at least in terms of concepts.
We now start constructing apparently new ideas that will allow us to formalize the concepts of an assembly space and the assembly index.
The first of these is the idea of a pathway.
Suppose you begin with a given object $x$ and wish to fleshout all of the ways in which a second object $y$ might be constructed.
The simplest first step is to construct a sequence of transitions, the first of which takes $x$ as part of its input, the last yields $y$ as part of it its output, and every transition in between depends at least partially on the output of the previous.
Such a sequence of transitions is what we refer to as a \textit{pathway}.

\begin{definition}\label{def:pathway}
    If $P$ is a Petri net, a \textbf{pathway} $\gamma = t_n \ldots t_1$ in $P$ of length $n \ge 1$ is a sequence of transitions $t_i \in T$ such that $\tau(t_i) \ne 0$, $\sigma(t_i) \ne 0$, $m_{i} + \tau(t_i) = n_{i+1} + \sigma(t_{i+1})$ with $\sigma(t_{i+1}) \ne m_{i}$ and $\tau(t_{i+1}) \ne n_{i+1}$. We write $t \in \gamma$ to denote that the transition $t$ appears in the pathway $\gamma$.
\end{definition}

It is clear that a pathway is a directed concept in general.
A pathway from $x$ to $y$ is not necessarily a pathway from $y$ to $x$, and the existence of a pathway from $x$ to $y$ does not imply a pathway from $y$ to $x$ exists.
If there is a pathway from $x$ to $y$ we say \textit{$x$ pathway connected to $y$}.
In general, if $x$ is pathway connected to $y$ there may be multiple pathways, and it will be useful to refer to that set of pathways.

\begin{definition}\label{def:pathway-connected}
    Let $P$ be a Petri net and $x,y \in S(P)$.
    We say that $x$ is \textbf{pathway connected to} $y$ if and only if there exists a pathway $\gamma = t_n \ldots t_1$ such that $\sigma(t_1) = x + m$ and $\tau(t_n) = y + n$ for some $m, n \in \N[S(P)]$.
    The set of all pathways in $P$ from $x$ to $y$ is denoted $\Gamma_x^y$.
    We denote the set of all pathways in $P$ starting from $x$ as $\Gamma_x = \bigcup_{y \in S(P)} \Gamma_x^y$, and all pathways terminating at $y$ as $\Gamma^y = \bigcup_{x \in S(P)} \Gamma_x^y$.
\end{definition}

In our ligation example, you might suppose that you begin with $A$ and would like to ultimately yield $AAAB$.
There are in fact two pathways which accomplish this, $\gamma\alpha$ and $\gamma\beta$, which we read as \textit{first fire $\alpha$ ($\beta$, respectively) and then fire $\gamma$}:
\begin{center}
    \scalebox{0.6}{
        \begin{tikzpicture}
            \begin{pgfonlayer}{nodelayer}
                \node [style=site] (A) at (0, 0.8) {$A$};
                \node [style=site] (B) at (0, -0.8) {$B$};
                \node [style=site] (C) at (6, -1.6) {$C$};
                \node [style=site] (AA) at (4, 0.8) {$AA$};
                \node [style=site] (AB) at (4, -0.8) {$AB$};
                \node [style=site] (AAAB) at (8, 0) {$AAAB$};
                \node [style=transition, fill=green!20] (tau1) at (2, 0.8) {$\alpha$};
                \node [style=transition] (tau2) at (2, -0.8) {$\beta$};
                \node [style=transition, fill=green!20] (tau3) at (6, 0) {$\gamma$};
                \node [style=transition] (tau4) at (10, 0) {$\delta$};
                \node [scale=3] at (5, -3.5) {$\gamma\alpha$};

                \node [style=site] (A2) at (14, 0.8) {$A$};
                \node [style=site] (B2) at (14, -0.8) {$B$};
                \node [style=site] (C2) at (20, -1.6) {$C$};
                \node [style=site] (AA2) at (18, 0.8) {$AA$};
                \node [style=site] (AB2) at (18, -0.8) {$AB$};
                \node [style=site] (AAAB2) at (22, 0) {$AAAB$};
                \node [style=transition] (tau12) at (16, 0.8) {$\alpha$};
                \node [style=transition, fill=green!20] (tau22) at (16, -0.8) {$\beta$};
                \node [style=transition, fill=green!20] (tau32) at (20, 0) {$\gamma$};
                \node [style=transition] (tau42) at (24, 0) {$\delta$};
                \node [scale=3] at (19, -3.5) {$\gamma\beta$};
            \end{pgfonlayer}
            \begin{pgfonlayer}{edgelayer}
                \draw [style=arrow, bend right=15] (A) to (tau1);
                \draw [style=arrow, bend left=15] (A) to (tau1);
                \draw [style=arrow, bend right=15] (A) to (tau2);
                \draw [style=arrow] (tau1) to (AA);
                \draw [style=arrow] (B) to (tau2);
                \draw [style=arrow] (tau2) to (AB);
                \draw [style=arrow] (AA) to (tau3);
                \draw [style=arrow] (AB) to (tau3);
                \draw [style=arrow, bend left=30] (C) to (tau3);
                \draw [style=arrow] (tau3) to (AAAB);
                \draw [style=arrow, bend left=30] (tau3) to (C);
                \draw [style=arrow] (AAAB) to (tau4);
                \draw [style=arrow, bend right=30] (tau4) to (A);
                \draw [style=arrow, bend right=30] (tau4) to (AA);
                \draw [style=arrow, bend left=40] (tau4) to (B);

                \draw [style=arrow, bend right=15] (A2) to (tau12);
                \draw [style=arrow, bend left=15] (A2) to (tau12);
                \draw [style=arrow, bend right=15] (A2) to (tau22);
                \draw [style=arrow] (tau12) to (AA2);
                \draw [style=arrow] (B2) to (tau22);
                \draw [style=arrow] (tau22) to (AB2);
                \draw [style=arrow] (AA2) to (tau32);
                \draw [style=arrow] (AB2) to (tau32);
                \draw [style=arrow, bend left=30] (C2) to (tau32);
                \draw [style=arrow] (tau32) to (AAAB2);
                \draw [style=arrow, bend left=30] (tau32) to (C2);
                \draw [style=arrow] (AAAB2) to (tau42);
                \draw [style=arrow, bend right=30] (tau42) to (A2);
                \draw [style=arrow, bend right=30] (tau42) to (AA2);
                \draw [style=arrow, bend left=40] (tau42) to (B2);
            \end{pgfonlayer}
        \end{tikzpicture}
    }
\end{center}
where the transitions involved in the pathway are colored green.
The set of pathways from $A$ to $AAAB$ is then $\Gamma_{A}^{AAAB} = \{ \gamma\alpha, \gamma\beta \}$.
In the case where there are loops in the Petri net, some or all of the sets of pathways will be countably infinite.
While this seems undesirable, it does not present much of a problem for the problems under consideration in this work.

As with subnets, pathways interact well with Petri net morphisms.
This brings us to our first lemma:
\begin{lemma}\label{lem:image-of-pathways}
    Let $f: P \rightarrow Q$ be a Petri net morphism and let $x, y \in S(P)$ be pathway connected in $P$.
    Then $f(x)$ and $f(y)$ are pathway connected in $f(P)$.
\end{lemma}
\begin{proof}
    Let $\gamma = t_n \ldots t_1$ be a pathway from $x$ to $y$.
    Given that $\sigma_P(t_i) \ne 0$ and $\tau_P(t_i) \ne 0$, we know that $\sigma_{f(P)} \ne 0$ and $\tau_{f(P)} \ne 0$.
    Since $\sigma_P(t_1) = x + m$, $\sigma_{f(P)}(f(x)) = f(x) + m'$ for some $m' \in \N[S(f(P))]$; similarly, $\tau_{f(P)}(f(y)) = f(y) + n'$ for some $n' \in \N[S(f(P))]$.

    Now, consider two transitions $t_i$ and $t_{i+1}$ in $\gamma$.
    We know then that there exist $m, n \in \N[S(P)]$ such that $m + \tau_P(t_i) = n + \sigma_P(t_{i+1})$ with $m \ne \sigma_P(t_{i+1})$ and $n \ne \tau_P(t_i)$.
    We can then apply $\N[S(f)]$ to each side to yield
    \begin{equation*}
        \N[S(f)](m) + \N[S(f)](\tau_P(t_i)) = \N[S(f)](n) + \N[S(f)](\sigma_P(t_{i+1})).
    \end{equation*}
    Per the commutativity relations imposed by the assembly map,
    \begin{equation*}
        \N[S(f)](\tau_P(t_i)) = \tau_{f(P)}(f(t_i)))
        \quad\textrm{and}\quad
        \N[S(f)](\sigma_P(t_{i+1})) = \sigma_{f(P)}(f(t_{i+1})).
    \end{equation*}
    So, there exist an $m', n' \in \N[S(f(P))]$ such that $m + \tau_{f(P)}(f(t_i)) = n + \sigma_{f(P)}(f(t_{i+1}))$, namely $m' = \N[S(f)](m)$ and $n' = \N[S(f)](n)$.
    Finally, we know that $m' \ne \sigma_{f(P)}(f(t_{i+1}))$ as otherwise $m = \sigma_P(t_{i+1})$, and similarly $n' \ne \tau_{f(P)}(f(t_i))$.

    This shows that a pathway exists from $f(x)$ to $f(y)$, so $f(x)$ and $f(y)$ are pathway connected.
\end{proof}

We can view a pathway in a given Petri net $P$ as, or rather use it to construct, a set of transitions.
This set of transitions does not, in and of itself, give us a Petri subnet; however, we can imagine collecting all of the sites in $P$ which participate in those transitions.
Recalling back to \cref{subsec:fcm}, we can use $\pi$ to determine the sites which participate in a given linear combination.
We can extend this idea to transitions in a Petri net.
\begin{definition}\label{def:participate}
    Let $P$ be a Petri net and let $t \in T(P)$ be a transition.
    The set of all sites which participate in $t$ is denoted $\rho(t) = \pi(\sigma(t)) \cup \pi(\tau(t))$.
    Similarly, if $X \subseteq T(P)$, $\rho(X) = \bigcup_{t \in X}\rho(x)$.
\end{definition}

This allows us to then define the \textit{site completion} of a subset of transitions from some Petri net.

\begin{definition}\label{def:site-completion}
    Let $P$ be a petri net and let $X \subseteq T(P)$.
    The \textbf{site completion} of $X$ in $P$, denoted $X^*$ is the Petri net defined by $T(X^*) = X$, $S(X^*) = \rho(X)$, $\sigma_{X^*} = \sigma_P|_{X^*}$ and $\tau_{X^*} = \tau_P|_{X^*}$.
\end{definition}
It is very clear from the definition that for any given set of transitions $X$, the site completion is a Petri subnet.
The site completion presents a very natural method for constructing a Petri subnet from a set of pathways, and gives a clean way of thinking about all of the different ways in which an object might be assembled from some starting set of objects.
Taking the paths $\gamma\alpha$, $\gamma\beta$ and the set $\Gamma_A^{AAAB}$ from the previous example, we can construct the following Petri subnets (highlighted in red):
\begin{center}
    \scalebox{0.6}{
        \begin{tikzpicture}
            \begin{pgfonlayer}{nodelayer}
                \node [style=site, draw=red] (A) at (0, 0.8) {$A$};
                \node [style=site] (B) at (0, -0.8) {$B$};
                \node [style=site, draw=red] (C) at (6, -1.6) {$C$};
                \node [style=site, draw=red] (AA) at (4, 0.8) {$AA$};
                \node [style=site, draw=red] (AB) at (4, -0.8) {$AB$};
                \node [style=site, draw=red] (AAAB) at (8, 0) {$AAAB$};
                \node [style=transition, fill=green!20, draw=red] (tau1) at (2, 0.8) {$\alpha$};
                \node [style=transition] (tau2) at (2, -0.8) {$\beta$};
                \node [style=transition, fill=green!20, draw=red] (tau3) at (6, 0) {$\gamma$};
                \node [style=transition] (tau4) at (10, 0) {$\delta$};
                \node [scale=3] at (5, -3.5) {$\rho(\gamma\alpha)^*$};

                \node [style=site, draw=red] (A2) at (14, 0.8) {$A$};
                \node [style=site, draw=red] (B2) at (14, -0.8) {$B$};
                \node [style=site, draw=red] (C2) at (20, -1.6) {$C$};
                \node [style=site, draw=red] (AA2) at (18, 0.8) {$AA$};
                \node [style=site, draw=red] (AB2) at (18, -0.8) {$AB$};
                \node [style=site, draw=red] (AAAB2) at (22, 0) {$AAAB$};
                \node [style=transition] (tau12) at (16, 0.8) {$\alpha$};
                \node [style=transition, fill=green!20, draw=red] (tau22) at (16, -0.8) {$\beta$};
                \node [style=transition, fill=green!20, draw=red] (tau32) at (20, 0) {$\gamma$};
                \node [style=transition] (tau42) at (24, 0) {$\delta$};
                \node [scale=3] at (19, -3.5) {$\rho(\gamma\beta)^*$};

                \node [style=site, draw=red] (A3) at (7, -5.2) {$A$};
                \node [style=site, draw=red] (B3) at (7, -6.8) {$B$};
                \node [style=site, draw=red] (C3) at (13, -7.6) {$C$};
                \node [style=site, draw=red] (AA3) at (11, -5.2) {$AA$};
                \node [style=site, draw=red] (AB3) at (11, -6.8) {$AB$};
                \node [style=site, draw=red] (AAAB3) at (15, -6) {$AAAB$};
                \node [style=transition, fill=green!20, draw=red] (tau13) at (9, -5.2) {$\alpha$};
                \node [style=transition, fill=green!20, draw=red] (tau23) at (9, -6.8) {$\beta$};
                \node [style=transition, fill=green!20, draw=red] (tau33) at (13, -6) {$\gamma$};
                \node [style=transition] (tau43) at (17, -6) {$\delta$};
                \node [scale=3] at (12, -9.5) {$\rho(\Gamma_A^{AAAB})^*$};
            \end{pgfonlayer}
            \begin{pgfonlayer}{edgelayer}
                \draw [style=arrow, bend right=15, draw=red] (A) to (tau1);
                \draw [style=arrow, bend left=15, draw=red] (A) to (tau1);
                \draw [style=arrow, bend right=15] (A) to (tau2);
                \draw [style=arrow, draw=red] (tau1) to (AA);
                \draw [style=arrow] (B) to (tau2);
                \draw [style=arrow] (tau2) to (AB);
                \draw [style=arrow, draw=red] (AA) to (tau3);
                \draw [style=arrow, draw=red] (AB) to (tau3);
                \draw [style=arrow, bend left=30, draw=red] (C) to (tau3);
                \draw [style=arrow, draw=red] (tau3) to (AAAB);
                \draw [style=arrow, bend left=30, draw=red] (tau3) to (C);
                \draw [style=arrow] (AAAB) to (tau4);
                \draw [style=arrow, bend right=30] (tau4) to (A);
                \draw [style=arrow, bend right=30] (tau4) to (AA);
                \draw [style=arrow, bend left=40] (tau4) to (B);

                \draw [style=arrow, bend right=15] (A2) to (tau12);
                \draw [style=arrow, bend left=15] (A2) to (tau12);
                \draw [style=arrow, bend right=15, draw=red] (A2) to (tau22);
                \draw [style=arrow] (tau12) to (AA2);
                \draw [style=arrow, draw=red] (B2) to (tau22);
                \draw [style=arrow, draw=red] (tau22) to (AB2);
                \draw [style=arrow, draw=red] (AA2) to (tau32);
                \draw [style=arrow, draw=red] (AB2) to (tau32);
                \draw [style=arrow, bend left=30, draw=red] (C2) to (tau32);
                \draw [style=arrow, draw=red] (tau32) to (AAAB2);
                \draw [style=arrow, bend left=30, draw=red] (tau32) to (C2);
                \draw [style=arrow] (AAAB2) to (tau42);
                \draw [style=arrow, bend right=30] (tau42) to (A2);
                \draw [style=arrow, bend right=30] (tau42) to (AA2);
                \draw [style=arrow, bend left=40] (tau42) to (B2);

                \draw [style=arrow, bend right=15, draw=red] (A3) to (tau13);
                \draw [style=arrow, bend left=15, draw=red] (A3) to (tau13);
                \draw [style=arrow, bend right=15, draw=red] (A3) to (tau23);
                \draw [style=arrow, draw=red] (tau13) to (AA3);
                \draw [style=arrow, draw=red] (B3) to (tau23);
                \draw [style=arrow, draw=red] (tau23) to (AB3);
                \draw [style=arrow, draw=red] (AA3) to (tau33);
                \draw [style=arrow, draw=red] (AB3) to (tau33);
                \draw [style=arrow, bend left=30, draw=red] (C3) to (tau33);
                \draw [style=arrow, draw=red] (tau33) to (AAAB3);
                \draw [style=arrow, bend left=30, draw=red] (tau33) to (C3);
                \draw [style=arrow] (AAAB3) to (tau43);
                \draw [style=arrow, bend right=30] (tau43) to (A3);
                \draw [style=arrow, bend right=30] (tau43) to (AA3);
                \draw [style=arrow, bend left=40] (tau43) to (B3);
            \end{pgfonlayer}
        \end{tikzpicture}
    }
\end{center}

\begin{definition}\label{def:upper-lower-subnet}
    Let $P$ be a Petri net and let $X \subseteq S(P)$.
    The \textbf{upper subnet} of $X$ in $P$, denoted $\upset{X}$, consists of transitions $T(\upset{X}) = \bigcup_{x \in X}\{t \in \gamma ~|~ \gamma \in \Gamma_x\}$, sites $S(\upset{X}) = X \cup S(T(\upset{X})^*)$, $\sigma_{X\uparrow} = \sigma_P|_{T(X\uparrow)^*}$ and $\tau_{X\uparrow} = \tau_P|_{T(X\uparrow)^*}$.
    Similarly, the \textbf{lower subnet} of $X$ in $P$, denoted $\downset{X}$, consists of transitions $T(\downset{X}) = \{t \in \gamma ~|~ \gamma \in \Gamma_X\}$, sites $S(\downset{X}) = X \cup S(T(\downset{X})^*)$, $\sigma' = \sigma|_{T(X\downarrow)^*}$ and $\tau = \tau|_{T(X\downarrow)^*}$.
    If $x$ is an element $x \in P$, we write $\upset{x} = \upset{\{x\}}$ and $\downset{x} = \downset{\{x\}}$.
\end{definition}

\begin{definition}\label{def:minimal}
    Let $P$ be a Petri net. A site $y$ is \textbf{minimal} in $P$ if $\Gamma_x^y = \emptyset$ for all sites $y \ne x$ in $P$.
    The set of all minimal sites of $P$ is denoted $\Min{P}$.
\end{definition}

\begin{definition}\label{def:basis}
    Let $P$ be a Petri net and let $\B$ be a non-empty subset of sites of $P$.
    We say that $\B$ is a \textbf{basis} of $P$ if $P = \upset{\B}$ such that if $U \subseteq \B$ with $P = \upset{U}$ then $U = \B$.
\end{definition}

\begin{lemma}
    Let $P$ be a Petri net. For any basis $\B$ of $P$, $\Min{P} \subseteq \B$.
    Furthermore, if $\Min{P}$ is a basis of $P$, then $\Min{P}$ is the unique basis of $P$.
\end{lemma}
\begin{proof}
    Let $x \in \Min{P}$ and $\B$ be a basis of $P$, then either there exists a $y \in \B$ such that $\Gamma_y^x$ is non-empty, or $x \in \B$.
    However, $\Gamma^x$ is empty by definition of $\Min{P}$, so we have that $x \in B$.
    Since the choice of $x$ was arbitrary, every element of $\Min{P}$ is in the basis $\B$ and thus $\min{P} \subseteq \B$.
    Furthermore, suppose that $P = \upset{\Min{P}}$.
    Then $\B = \Min{P}$, otherwise $\B$ would not be a basis, by definition.
    Since $\B$ was chosen arbitrarily, this holds for every choice of $\B$ and as such $\Min{P}$ is a unqiue basis for $P$.
\end{proof}

\begin{lemma}\label{lem:image-basis}
    Let $P$ be a Petri net with basis $\B$ and let $f : A \rightarrow B$ be a Petri net morphism.
    Then $f(\B)$ is a basis for $f(P)$.
\end{lemma}
\begin{proof}
    Certainly $f(\B)$ is nonempty as $\B$ is nonempty, and of course $f(P)$ must be in the upper set of $f(\B)$.
    This follows immediately from \cref{lem:image-of-pathways} since every site in $P$ is pathway connected to a site in $\B$.
    Now let $U \subset f(\B)$ such that $f(P) = \upset{U}$.
    \TODO{Show that $f(\B)$ is minimal.}
\end{proof}

@@

\begin{lemma}\label{lem:lower-is-rooted}
    Let $A$ be an assembly space and let $x \in S(A)$.
    Then $\downset{x}$ with basis $\B_A \cap S(\downset{x})$ is a rooted assembly subspace of $A$.
\end{lemma}
\begin{proof}
    By construction, $\downset{x}$ is a Petri subnet of $A$.
    Since $A$ is an assembly space, it is sourceless and sinkless; and given that $\downset{x}$ is a site-completion, $\downset{x}$ is also sourceless and sinkless.
    This gives us that $\downset{x}$ is an assembly subspace of $A$.
    We need only show that $\B_{x\downarrow} = \B_A \cap S(\downset{x}) \subseteq \B_A$ is a basis of $\downset{x}$.
    First, $\B_{x\downarrow}$ is necessarily nonempty since $\B_A$ is a basis in $A$.
    Further, we know that every site in $\downset{x}$ is above $\B_A \cap S(\downset{x})$ since, again $\B_A$ is a basis in $A$.
    \TODO{Show that $\B_{x\downarrow}$ is minimal.}
\end{proof}

@@

\begin{theorem}\label{lem:assembly-image-is-subspace}
    If $f : A \rightarrow B$ is an assembly map between assembly spaces $A$ and $B$, then $f(A)$ is an assembly subspace of $B$.
\end{theorem}
\begin{proof}
    This follows directly from the fact that the image of a Petri net morphism is a Petri subnet, and that the image of a sourceless, sinkless Petri net is itself sourceless and sinkless.
\end{proof}

\begin{theorem}\label{thm:rooted-image}
    Let $A$ be an assembly space, $Z \subseteq A$ a rooted assembly subspace, and $f : A \rightarrow B$ an assembly map.
    Then $(f(Z), S(f)(\B_Z))$ is rooted in $(f(A), S(f)(\B_A)$.
\end{theorem}
\begin{proof}
    First, $f(Z)$ is certainly an assembly subspace of $f(A)$ as we can view $f|_Z$ as an assembly map, and thus \cref{lem:assembly-image-is-subspace} applies.
    To see that $f(Z)$ is rooted, we first note that $S(f)(\B_Z)$ and $S(f)(\B_A)$ are bases for $f(Z)$ and $f(A)$, respectively.
    Further, since $Z$ is rooted in $A$, then $\B_Z \subset \B_A$, so $f(\B_Z) \subseteq f(\B_A)$.
\end{proof}

@@

\begin{theorem}\label{cor:subspace-index-upper-bound}
    Let $(A, \B_A)$ be an assembly space and let $(B, \B_A)$ be a rooted assembly subspace of $A$.
    For every finite $b \in S(B)$, the assembly index of $b$ in $B$ is at least the assembly index of $b$ in $A$.
    That is, $c_B(b) \ge c_A(b)$ for all $b \in S(B)$
\end{theorem}
\begin{proof}
    We need only show that $c_A(b)$ cannot be greater than $c_B(b)$ for any $b \in S(B)$.
    To see this, let $Z \subseteq B$ be a rooted assembly subspace containing $b$ with $|Z| = c_B(b)$.
    Then $Z$ is also a rooted assembly subspace of $A$ containing $b$, and so $c_A(b)$ can be at most $|Z|$.
    That is, $c_A(b) \le |Z| = c_B(b)$.
\end{proof}

>>>>

\tikzstyle{arrow}=[-,postaction={decorate},decoration={markings,mark=at position .5 with {\arrow{>}}},line width=1.100]
\pgfdeclarelayer{edgelayer}
\pgfdeclarelayer{nodelayer}
\pgfsetlayers{edgelayer,nodelayer,main}

@@

\tikzstyle{empty}=[circle, fill=none, draw=none]
\tikzstyle{inputdot}=[circle, fill=black, draw=black, scale=.5]
\tikzstyle{dot}=[circle, fill=black, draw=black]
\tikzstyle{bounding}=[circle, dashed, fill=none, draw=black, scale=9.00]
\tikzstyle{simple}=[->, draw=black, line width=1]
\tikzstyle{arrow}=[-, draw=black, postaction={decorate}, decoration={markings,mark=at position .5 with {\arrow{>}}}, line width=1.000]
\tikzstyle{tick}=[-, draw=black, postaction={decorate}, decoration={markings,mark=at position .5 with {\draw (0,-0.1) -- (0,0.1);}}, line width=1.000]
\tikzstyle{inputarrow}=[->, draw=black, shorten >=.05cm]
\tikzstyle{sitemap}=[->, dashed, draw=red, ultra thick, shorten >=.05cm]
\tikzstyle{transitionmap}=[->, dashed, draw=blue, ultra thick, shorten >=.05cm]

@@

\newcommand{\upset}[1]{#1\!\!\uparrow}
\newcommand{\downset}[1]{#1\!\!\downarrow}
\newcommand{\N}{\mathbb{N}}
\newcommand{\B}{\mathcal{B}}
\newcommand{\Min}[1]{\min{(#1)}}
\newcommand{\Max}[1]{\max{(#1)}}
\newcommand{\Minim}{\mathcal{Min}}
\newcommand{\Maxim}{\mathcal{Max}}
\newcommand{\A}{\mathcal{A}}
\newcommand{\powerset}{\mathcal{P}}
\newcommand{\pathway}[1]{\langle~#1~\rangle}

\newcommand{\red}[1]{{\color{red}#1}}
\newcommand{\green}[1]{{\color{green}#1}}
\newcommand{\blue}[1]{{\color{blue}#1}}
\newcommand{\TODO}[1]{\noindent\red{\textbf{TODO:}~#1}}

@@

\red{Describe the relationship between the $\pi$ notation and the addition operator since we use both in subsequent sections.}

@@

\begin{definition}\label{def:subnet}
    Let $Q$ be a Petri net. A \textbf{Petri subnet} $P$ of $Q$ consists of
    \begin{itemize}
        \item a subset of sites of $Q$, denoted $S(P)$
        \item a subset of transitions of $Q$, denoted $T(P)$
        \item a pair of maps $\begin{tikzcd}
                T(P)
                \arrow[r, shift left = 1, "\sigma_P"]
                \arrow[r, shift right = 1, "\tau_P", swap]
                &
                \N[S(P)]
        \end{tikzcd}$.
    \end{itemize}
    such that $\sigma_P = \sigma_Q|_{T(P)}$ and $\tau_P = \tau_Q|_{T(P)}$.
    We denote this relationship as $P \subseteq Q$.
\end{definition}

@@

\begin{definition}
    Let $P$ be a Petri net and let $Q \subseteq P$.
    We say that $Q$ \textit{spans} $P$ if $S(Q) = S(P)$.
    \TODO{New Definition. Integrate with surrounding text.}
\end{definition}

@@

Up to this point, all of the defintions have been fairly standard, at least in terms of concepts.
We now start constructing apparently new ideas that will allow us to formalize the concepts of an assembly space and the assembly index.
The first of these is the idea of a pathway.
Suppose you begin with a given object $x$ and wish to fleshout all of the ways in which a second object $y$ might be constructed.
The simplest first step is to construct a sequence of transitions, the first of which takes $x$ as part of its input, the last yields $y$ as part of it its output, and every transition in between depends at least partially on the output of the previous.
Such a sequence of transitions forms the core of what we refer to as a \textit{pathway}.

\begin{definition}\label{def:pathway}
    Let $P$ be a Petri net.
    A \textbf{pathway} in $P$ is a sequence of transitions $\gamma = \pathway{t_n \ldots t_1}$ of length $n \ge 1$ such that for all $1 \le i \le n$
    \begin{equation*}
        \pi(\sigma(t_i)) \subseteq \bigcup_{j=1}^{i-1} \pi(\tau(t_j)).
    \end{equation*}
    We consider the empty sequence of transitions as a pathway and refer to it as the \textbf{zero pathway}.

    \smallskip
    Let $X$ be a subset of sites in $P$. We say that $\gamma$ is \textit{from $X$} if $\pi(\sigma(t_1)) \subseteq X$.

    \smallskip
    Let $y$ be site, and let $Y$ be a subset of sites.
    We say $\gamma$ is a \textit{to $y$} if $y \in \pi(\tau(t_n))$, and \textit{to $Y$} if $Y \subseteq \pi(\tau(t_n))$.

    \smallskip
    We say that the zero pathway is a pathway from any set $X$ to itself and none other.

    \smallskip
    Let $X$ and $Y$ be sets of sites in $P$.
    We say $X$ is \textbf{pathway connected} to $Y$ if there exists a pathway, possibly the zero pathway, from $X$ to $Y$.

    \red{I'd rather express this idea using $\N$ directly instead of using $\pi$}

    \TODO{Break this definition apart}
\end{definition}

\red{The definition above is very close to the definition of a firing sequence. The primary difference is that we have no number-preserving requirements.}

\begin{lemma}\label{lem:image-of-pathways}
    Let $f: P \rightarrow Q$ be a Petri net morphism and let $X, Y \subseteq S(P)$ be pathway connected in $P$.
    Then either $f(x)$ and $f(y)$ are pathway connected in $f(P)$.
\end{lemma}
\begin{proof}
    \TODO{Complete}
\end{proof}

\begin{definition}\label{def:site-completion}
    \TODO{Complete}
\end{definition}

\begin{definition}\label{def:generator}
    \TODO{A set of sites from which there is a pathway to every other object}
\end{definition}

\begin{definition}\label{def:basis}
    Let $P$ be a Petri net and $X \subseteq S(P)$.
    We say that $X$ is a basis of $P$ if $\ldots$.
    \TODO{Complete}
\end{definition}

\begin{lemma}\label{lem:minimal-are-basic}
    Let $P$ be a Petri net. For any basis $\B$ of $P$, $\Min{P} \subseteq \B$.
\end{lemma}
\begin{proof}
    \TODO{Complete}
\end{proof}

\begin{lemma}\label{lem:image-basis}
    Let $P$ be a Petri net with basis $\B$ and let $f : A \rightarrow B$ be a Petri net morphism.
    Then $f(\B)$ is a basis for $f(P)$.
\end{lemma}
\begin{proof}
    \TODO{Complete}
\end{proof}

@@

\begin{lemma}\label{lem:lower-is-rooted}
    Let $A$ be an assembly space and let $x \in S(A)$.
    Then $\downset{x}$ with basis $\B_A \cap S(\downset{x})$ is a rooted assembly subspace of $A$.
\end{lemma}
\begin{proof}
    \TODO{Complete}
\end{proof}

@@

\begin{theorem}\label{lem:assembly-image-is-subspace}
    If $f : A \rightarrow B$ is an assembly map between assembly spaces $A$ and $B$, then $f(A)$ is an assembly subspace of $B$.
\end{theorem}
\begin{proof}
    \TODO{Complete}
\end{proof}

\begin{theorem}\label{thm:rooted-image}
    Let $A$ be an assembly space, $Z \subseteq A$ a rooted assembly subspace, and $f : A \rightarrow B$ an assembly map.
    Then $(f(Z), S(f)(\B_Z))$ is rooted in $(f(A), S(f)(\B_A)$.
\end{theorem}
\begin{proof}
    \TODO{Complete}
\end{proof}

@@

\begin{theorem}\label{cor:subspace-index-upper-bound}
    Let $(A, \B_A)$ be an assembly space and let $(B, \B_A)$ be a rooted assembly subspace of $A$.
    For every finite $b \in S(B)$, the assembly index of $b$ in $B$ is at least the assembly index of $b$ in $A$.
    That is, $c_B(b) \ge c_A(b)$ for all $b \in S(B)$
\end{theorem}
\begin{proof}
    \TODO{Complete}
    % We need only show that $c_A(b)$ cannot be greater than $c_B(b)$ for any $b \in S(B)$.
    % To see this, let $Z \subseteq B$ be a rooted assembly subspace containing $b$ with $|Z| = c_B(b)$.
    % Then $Z$ is also a rooted assembly subspace of $A$ containing $b$, and so $c_A(b)$ can be at most $|Z|$.
    % That is, $c_A(b) \le |Z| = c_B(b)$.
\end{proof}
